---
title: "Management API"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Management API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(auth0)
```

The [Auth0 Management API](https://auth0.com/docs/manage-users/user-accounts/manage-users-using-the-management-api) allows interacting with users. The first step is to create a [Machine-to-Machine]()https://auth0.com/docs/get-started/auth0-overview/create-applications/machine-to-machine-apps application which will have its own client and secret. This client and secret will be the credentials used to retrieave OAuth tokens and interact with the management API. 

The _auth0.yml will need to be edited to contain the machine to machine credentials:

```{yaml}
name: My App
remote_url: ''
auth0_config:
  api_url: !expr paste0('https://', Sys.getenv('AUTH0_USER'), '.us.auth0.com')
  credentials:
    key: !expr Sys.getenv("AUTH0_KEY")
    secret: !expr Sys.getenv("AUTH0_SECRET")
  management:
    key: !expr Sys.getenv("AUTH0_MGMT_KEY")
    secret: !expr Sys.getenv("AUTH0_MGMT_SECRET")
```

From here, you can use the user_id from the session$userData object to call and modify additional information about a user. 

```{r, eval=FALSE}

user_id = session$userData$sub
auth0_user_management(user_id, "get")
auth0_user_management(user_id, "update", user_metadata = list(config = list(theme = "dark", last_tab = "settings")))
```

