---
title: "Management API"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Management API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(auth0)
```

The [Auth0 Management API](https://auth0.com/docs/manage-users/user-accounts/manage-users-using-the-management-api) allows interacting with users. The first step is to create a [Machine-to-Machine]()https://auth0.com/docs/get-started/auth0-overview/create-applications/machine-to-machine-apps application which will have its own client and secret. This client and secret will be the credentials used to retrieave OAuth tokens and interact with the management API. 

After logging in with the auth0, you can use the user_id from the session$userData object to call and modify additional information about a user. 

```{r, eval=FALSE}
user_id = session$userData$sub
auth0_user_management(user_id, "get")
auth0_user_management(user_id, "update", user_metadata = list(config = list(theme = "dark", last_tab = "settings")))
```

